Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-24 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

\usepackage{bm,bbm,bbding}
\usepackage{natbib}
\usepackage{siunitx}
\usepackage{texnames}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
	\savestack{\tmpbox}{\stretchto{%
			\scaleto{%
				\scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
				{\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
			}{\textheight}% 
		}{0.5ex}}%
	\stackon[1pt]{#1}{\tmpbox}%
}
\parskip 1ex

@@

\alert{They are different! Check \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics} for details.} Therefore, some empirical version of~\eqref{E:E-gamma} could be used to form a test statistic.

@@

@@

\begin{frame}[standout]
\frametitle{Takeaways}
You may forget about the technical contents of this talk, but remember:
\begin{itemize}[<+->]
	\item No problem is too old to be revisited.
	\item The data statistical properties always bring valuable information.
	\item A careful mathematical manipulation often leads to new exciting results.
	\item Reproducibility goes a long way!
\end{itemize}
\end{frame}

>>>>

\usepackage{bm,bbm}
\usepackage{natbib}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{mathabx}
\usepackage{scalerel,stackengine}
\stackMath
\newcommand\reallywidehat[1]{%
	\savestack{\tmpbox}{\stretchto{%
			\scaleto{%
				\scalerel*[\widthof{\ensuremath{#1}}]{\kern-.6pt\bigwedge\kern-.6pt}%
				{\rule[-\textheight/2]{1ex}{\textheight}}%WIDTH-LIMITED BIG WEDGE
			}{\textheight}% 
		}{0.5ex}}%
	\stackon[1pt]{#1}{\tmpbox}%
}
\parskip 1ex

@@

As expected, $H_{G_I^0}(\mu, \alpha, L)\to H_{\Gamma_{\text{SAR}}}(L, \mu)$ when $\alpha\to-\infty$.
\alert{But they are different!}
Check \citet{IdentifyingHeterogeneityinSARDatawithNewTestStatistics} for details.

Therefore, some empirical version of~\eqref{E:E-gamma} could be used to form a test statistic.

@@

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
	\begin{frame}{What we want to measure}
		\centering
\includegraphics[width=0.78\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_GI0_to_gamma1-1}
	\end{frame}
}

@@

\begin{frame}[standout]
\frametitle{Takeaways}
You may forget about the technical contents of this talk, but remember:
\begin{itemize}[<+->]
	\item No problem is too old to be revisited.
	\item The data statistical properties always bring valuable information.
	\item A careful mathematical manipulation often leads to new exciting results.
	\item The reproducible article (including these slides) is available \href{https://github.com/rjaneth/identifying-heterogeneity-in-sar-data-with-new-test-statistics}{\alert{here}}. Reproducibility goes a long way!
\end{itemize}
\end{frame}
